
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "Tesis"
%%% End:

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\setstretch{1.3} % Reset the line-spacing to 1.3 for body text (if it has changed)

\acknowledgements{\addtocontents{toc}{\vspace{1em}} % Add a gap in the Contents, for aesthetics

  I  thank to the members of this thesis committee:
  Dr. Rodrigo Huerta Quintanilla and Dr. Román Castro Rodriguez.

  The completion of this project could not have been accomplished without the
  support of my supervisors, Jesus Guillermo Contreras Nuño and Frank Zimmermann.

  I thank Consejo de Ciencia y Tecnología (CONACYT) and CINVESTAV for the
  financial support during my PhD. studies. I also thank CERN for all the
  information they make available to students such as myself.

  I thank the 'BEAMS' programme and ARIES for their grants and financial support
  during my visit at CERN.

  I also want to thank the administrative personnel from CINVESTAV Mérida which
  has been helpful and efficient, specially Dra. Cristina Vargas, Dr. Geonel
  Rodriguez and Zhirnay
  Rodriguez; As well as CERN's administrative personnel, specially Alessia and
  Delphine Reviron.

  I thank my whole section, HSS, for so many useful discussions, with a special
  mention to Massimo Giovannozzi, Rogelio Tomás, and Laurent Deniau.

  I thank several people at CERN who helped me understand the electron cloud
  phenomena and effects. Amongst them Lotta Mether, Giovanni Iadarola, and Giovanni
  Rumolo. 
  
  I am very grateful with CLASSE which made some computational resources
  available to me. I cannot express enough gratitude to David Sagan, who helped
  in all stages with the use of \srthree{}: from building, to  support and
  debugging. I thank James Crittenden and Stephen Popprocki who broadened my
  vision regarding interactions between photons and technical vacuum chamber surfaces. 

  A special acknowledgment to the team of experimentalists at Instituto
  Nazionale di Fisisca Nucleare, Laboratori Nazionali di Frascati. Roberto
  Cimino, Eliana La Francesca, Marco Angelucci, Ignasi Bellafont among others. 
}
\clearpage % Start a new page

