% Chapter 1

\chapter{Introduction} % Main chapter title

\label{intro} % For referencing the chapter elsewhere, use \ref{Chapter1} 

\lhead{Chapter 1. \emph{Introduction}} % This is for the header on each page - perhaps a shortened title


Synchrotron Radiation (SR) \rojo{I have a section of abbreviations, should I
  define them anyway the first time they appear?} emission is the phenomenon
product of the change of direction of relativistic-charged particles.  Ever
since it was observed in 1947 at the G.E. Synchrotron, \azul{cite required} the
interest in its study has increased, even though great part of the theory was
developed before that, and it is still being developed at the present (after a
hundred years).

In electron storage rings and circular accelerators, the emitted synchrotron
radiation reaches high intensities and energies. Although, Nowadays, there are
dedicated electron accelerators with the purpose of producing SR with specific
characteristics; in many other accelerators, S.R. is considered a secondary
product which is nocuous to the operation of the machine.

The power of emitted S.R.\rojo{should Accronims and abreviations use dots or
  not? e.g. SR or S.R.} depends on the square of the Lorentz factor
(\(\gamma_r^{2}\)). For this reason, S.R. was considered negligible in hadron
accelerators. It was until the construction of LHC, that hadron S.R. became a
problem for protons with a \(\gamma_r^{2}\geq 7460\) that the negative effects of
S.R. were not negligible. The LHC is the coldest place in the universe, in order
to keep the superconductor magnetic coils at 1.9 °K, gigantic cryogenic plants
are used because of the arc S.R. heat load of 0.17 W/m/aperture. The vacuum in
the LHC is as low as interestellar vacuum \(~10^{-14}\) bar, high-energy photons
from S.R. can remove molecules and particles from the wall, degrading this
vacuum.  Yet another problem related to S.R. is the formation of electron
clouds. These clouds could grow from seed electrons torn from the wall by
incident photons, these electrons are attracted by the proton beam and also
follow the magnetic field lines. Electron-cloud problems are the main motivation
for these studies.

The main objective of this work is to map the absorption points of S.R. photons
in the arcs of the LHC, with the idea that this map could be used in the future
to generate a photon distribution function (P.D.F.) to be used as an input for
electron-cloud simulations. To make this map we use the code Synrad3D developed
at Cornell which generates and tracks synchrotron-radiation photons in an
accelerator beam line, including specular and diffuse reflection on the chamber
surface.  The photons are generated randomly in any bending field, with initial
parameters determined by the local beam distribution, the local electromagnetic
field, and by the beam energy.  When a photon hits the chamber wall its
reflection probability depends on the energy and angle of incidence, as well as
on the material, including combinations of multiple layers, and on the surface
roughness.

The first chapter of this thesis is devoted to the most basic introduction to
accelerator design \rojo\{a lo mejor accelerator design no es la mejor forma de
decirlo, basics of accelerators o algo asi, semblance quizá\} and then it
presents some features \rojo{a lo mejor en vez de some features, usar the
  description} of the highest-energy circular colliders where our analysis was
implemented.

We then present in the second chapter a qualitative description of S.R. \rojo\{a
lo mejor poner explícito synchrotron radiation\} for a further understanding of
it, the author recommends going through chapters 1, 2 and 3 of "Synchrotron
Radiation" by A. A. Sokolov. \rojo{should I say this?\ldots also mention jackson
  cap 14? how do i make teh reference?} and its relation to E.C. build-up.

A description of the code Synrad3D is given in the third chapter. This is the
code we use for all simulations described in this thesis. Also, some tests and
benchmarking of the code will be mentioned.

Finally, in the last two chapters, we present our simulations, and the
implications they have to the previously mentioned accelerators.


%----------------------------------------------------------------------------------------

%\section{sexion}
